---
title: "Image - Image Overview"
author: "Fernando Prudencio"
date: '2020-01-06'
output:
  html_document:
    df_print: paged
  pdf_document: default
categories: image
type: post
url: /image_01/
w3codecolor: yes
thumbnail: https://user-images.githubusercontent.com/16768318/103680296-3fd3f700-4f86-11eb-8750-5a5920a87d18.png
tags:
- ee$Image
- ee$ImageCollection
---

**Adapted from [Google Earth Engine Documentation](https://developers.google.com/earth-engine/best_practices).**

This doc describes coding practices that are intended to maximize the chance of success for complex or expensive Earth Engine computations.

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'), tooltip_message = 'Click to copy', tooltip_success = 'Done', all_precode = TRUE)
```


```{r, setup, include=FALSE}
knitr::opts_chunk$set(
  comment = '', fig.width = 6, fig.height = 6
)
```

**Table of contents**

* **ee.Imagen constructor**
* **Get an ee. Imagen from an ee.ImageCollection**
* **Images from Cloud GeoTIFFs**
* **Constants images**

As mentioned in the [**Get Started**](https://developers.google.com/earth-engine/guides/getstarted#earth-engine-data-structures) doc, raster data are represented as `Image` objects in Earth Engine. Images are composed of one or more bands and each band has its own name, data type, scale, mask and projection. Each image has metadata stored as a set of properties.

### 1. ee.Image constructor

Images can be loaded by pasting an Earth Engine asset **ID** into the `ee$Image` constructor. You can find image **IDs** in the [**data catalog**](https://developers.google.com/earth-engine/datasets). For example, to load [**JAXA's ALOS DSM**](https://developers.google.com/earth-engine/datasets/catalog/JAXA_ALOS_AW3D30_V2_2):


```{r eval = FALSE}
library(rgee)
ee_Initialize()
srtm <- ee$Image("USGS/SRTMGL1_003")
```

### 2. Get an ee.Image from an ee.ImageCollection

The standard way to get an image out of a collection is to filter the collection, with filters in order of decreasing specificity. For example, to get an image out of the [**Sentinel-2 surface reflectance collection**](Sentinel-2 MSI: MultiSpectral Instrument, Level-1C):

```{r eval = FALSE}
# Load an image collection
sen <- ee$ImageCollection("COPERNICUS/S2")$
  filterBounds(ee$Geometry$Point(-70.48, 43.3631))$
  filterDate('2019-01-01', '2019-12-31')$
  sort('CLOUDY_PIXEL_PERCENTAGE')$
  first()

# Define the visualization parameters.
vizParams <- list(
  bands = c("B4", "B3", "B2"),
  min = 0,
  max = 2000,
  gamma = c(0.95, 1.1, 1)
)

# Center the map and display the image.
Map$centerObject(sen, 11)
# You can see it
Map$addLayer(sen, vizParams, 'first')
```
Note that the sort is after the filters. Avoid sorting the entire collection.

### 3. Images from Cloud GeoTIFFS
You can use `ee$Image$loadGeoTIFF()` to load images from [**Cloud Optimized GeoTIFFs**](https://github.com/cogeotiff/cog-spec/blob/master/spec.md) in [**Google Cloud Storage**](https://cloud.google.com/storage). For example, the [**public Landsat dataset**](https://console.cloud.google.com/marketplace/details/usgs-public-data/landast?pli=1) hosted in Google Cloud contains [**this GeoTIFF**](https://console.cloud.google.com/storage/browser/_details/gcp-public-data-landsat/LC08/01/001/002/LC08_L1GT_001002_20160817_20170322_01_T2/LC08_L1GT_001002_20160817_20170322_01_T2_B5.TIF), corresponding to band 5 from a Landsat 8 scene. You can load this image from Cloud Storage using `ee$Image$loadGeoTIFF()`:

```{r eval = FALSE}
uri <- sprintf(
  "%1s%2s%3s",
  "gs://gcp-public-data-landsat/LC08/01/001/002/",
  "LC08_L1GT_001002_20160817_20170322_01_T2/",
  "LC08_L1GT_001002_20160817_20170322_01_T2_B5.TIF"
)

cloudImage <- ee$Image$loadGeoTIFF(uri)

print(cloudImage)
```
Note that if you want to reload a Cloud Optimized GeoTIFF that you [**export from Earth Engine to Cloud Storage**](https://developers.google.com/earth-engine/guides/exporting#to-cloud-storage), when you do the export, set cloudOptimized to true as described [**here**](https://developers.google.com/earth-engine/guides/exporting#configuration-parameters).

### 4. Constants images
In addition to loading images by **ID**, you can also create images from constants, lists or other suitable Earth Engine objects. The following illustrates methods for creating images, getting band subsets, and manipulating bands:

```{r eval = FALSE}
library(rgee)

ee_Initialize()

# Create a constant Image with a pixel value of 1.
image1 <- ee$Image(1)
print(image1, type = "json")
print(image1, type = "simply")
print(image1, type = "ee_print")
# You can see it.
Map$addLayer(image1)

# Concatenate two Images into one multi-band image.
image2 <- ee$Image(2)
image3 <- ee$Image$cat(c(image1, image2))
ee_print(image3, clean = TRUE)

# Change print option by: "simply","json","ee_print"
options(rgee.print.option = "simply")

# Create a multi-band image from a list of constants.
multiband <- ee$Image(c(1, 2, 3))
print(multiband)

# Select and (optionally) rename bands.
renamed <- multiband$select(
  opt_selectors = c("constant", "constant_1", "constant_2"), # old names
  opt_names = c("band1", "band2", "band3")                   # new names
)
ee_print(renamed)

# Add bands to an image.
image4 <- image3$addBands(ee$Image(42))
print(image4)
```
